CrystalPlan: an Experiment Planning Tool for Crystallography

### 2010-12-30 docs/CrystalPlan_paper/paper.tex
Refs #182: Last couple of references added.

Existing diffraction experiment planning software programs (for example,
CrysAlis Pro from Oxford Diffraction; COSMO from Bruker AXS) were designed for
X-ray experiments where the crystal is rotated stepwise through the Bragg
diffraction condition using a single incident wavelength, 
resulting in a large number of sample orientations.
These programs are not suitable for TOPAZ, since as a time-of-flight instrument
(time-resolved Laue), it is collecting data from a wide
bandwidth of incident neutrons, contracting the Ewald sphere through the
reflection condition thus while keeping a crystal stationary, as described in
[!!!! CC WILSON REFERENCE].
 Additionally, this means that relatively few sample
orientations are needed in order to complete a measurement: whereas an X-ray measurement might have
hundreds or thousands of individual frames, a TOPAZ run may have as few as 10
to cover the same volume of reciprocal space.

@@

\begin{itemize}
  \item Load an instrument geometry file.
  \item Calculate the orientation of a crystal at different goniometer settings.
  \item Calculate the coverage of these orientations in reciprocal space,
  in volume and for single peaks.
  \item Take crystal Bravais lattice symmetries and the higher redundancy of
  higher space groups into account.
  \item Optimize the experiment plan automatically.
  \item Compare predicted and actual measurement of peaks.
\end{itemize}

>>>>

Existing diffraction experiment planning software programs (for example,
CrysAlis Pro from Oxford Diffraction; COSMO from Bruker AXS) were designed for
X-ray experiments where the crystal is rotated stepwise through the Bragg
diffraction condition using a single incident wavelength, 
resulting in a large number of sample orientations.
These programs are not suitable for TOPAZ, since as a time-of-flight instrument
(time-resolved Laue), it is collecting data from a wide
bandwidth of incident neutrons, contracting the Ewald sphere through the
reflection condition thus while keeping a crystal stationary, as described in
\cite{Schultz94,Wilson00}.
 Additionally, this means that relatively few sample
orientations are needed in order to complete a measurement: whereas an X-ray measurement might have
hundreds or thousands of individual frames, a TOPAZ run may have as few as 10
to cover the same volume of reciprocal space.

@@

\begin{itemize}
  \item Load a geometry file for a specific instrument (using a generic,
  flexible file format).
  \item Calculate the orientation of a crystal at different goniometer settings.
  \item Calculate the coverage of these orientations in reciprocal space,
  in volume and for single peaks.
  \item Take crystal Bravais lattice symmetries and the higher redundancy of
  higher space groups into account.
  \item Optimize the experiment plan automatically.
  \item Compare predicted and actual measurement of peaks.
\end{itemize}
